\pkg{Rgbp}: An R Package for Gaussian, Poisson, and Binomial Hierarchical Modeling

### 2013-11-06 jss/article.tex
edit

Note that the variance in (\ref{gammaprior}) is linear in the mean, whereas a slightly different Poisson-Gamma specification \citep{1997} has been used elsewhere e.g. that makes the variance in (\ref{gammaprior}) quadratic.

@@

In the other two cases, Poisson and Binomial, the flat prior distribution on $\frac{1}{r}$ induces the same improper prior distribution on shrinkages ($\pi(B_{j})\propto B_{j}^{-2} d B_j$) as does $A$ with Uniform($0, \infty$) for the Gaussian. As for the posterior propriety, we found that the resultant posterior distribution for the Binomial model is proper if there are at least two groups (among $k$ groups), whose observed values ($z_{j}$) are neither 0 nor $n_j$,  and the covariate matrix ($X_{(k\times m )}$) has a full rank ($rank(X)=m$). The Poisson model, however, can have such posterior propriety if there are two groups whose observed values are greater than 0 and the second-level mean ($\lambda_0$) is known. The efficiency of these priors is explored in the examples in section 5.

>>>>

Note that the variance in (\ref{gammaprior}) is linear in the mean, whereas a slightly different Poisson-Gamma specification \citep{1997} has been used elsewhere e.g. that makes the variances in (\ref{gammaprior}) and (\ref{gammapost}) quadratic functions of the mean respectively.

@@

In the other two cases, Poisson and Binomial, the flat prior distribution on $\frac{1}{r}$ induces the same improper prior distribution on shrinkages ($\pi(B_{j})\propto B_{j}^{-2} d B_j$) as does $A$ with Uniform($0, \infty$) for the Gaussian. As for the posterior propriety, we found that the resultant posterior distribution for the Binomial model is proper if there are at least two groups (among $k$ groups), whose observed values ($z_{j}$) are neither 0 nor $n_j$,  and the covariate matrix ($X_{(k\times m )}$), if any,  has a full rank ($rank(X)=m$). The Poisson model, however, can have such posterior propriety if there are two groups whose observed values are greater than 0 and the second-level mean ($\lambda_0$) is known. The efficiency of these priors is explored in the examples in section 5.
